---
title: "Ramsar Site Biodiversity Report"
subtitle: "`r params$site_name`"
author: "Muddymetrics Pipeline"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cosmo
    highlight: pygments
    toc: true
    toc_float: true
params:
  site_id: NA
  site_name: NA
  country: NA
  data_dir: NA
  output_dir: NA
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(leaflet)
library(viridis)

site_id <- params$site_id
site_name <- params$site_name
country <- params$country
data_dir <- params$data_dir
output_dir <- params$output_dir
```

# Site Information

| Field | Value |
|-------|-------|
| **Site ID** | `r site_id` |
| **Site Name** | `r site_name` |
| **Country** | `r country` |
| **Report Date** | `r Sys.Date()` |

---

# Data Sufficiency Assessment

This section presents the Troia 2016 data sufficiency indicators for `r site_name`.

## Key Metrics

```{r load-indicators, include=FALSE}
indicator_files <- list.files(
  file.path(output_dir, country, gsub(".*_", "", site_id)),
  pattern = paste0(gsub(".*_", "", site_id), ".*\\.RData$"),
  full.names = TRUE
)

density_val <- NA
obs_richness <- NA
total_occ <- NA
chao2_val <- NA

for (f in indicator_files) {
  tryCatch({
    load(f)
    if (exists("density_obj") && is.list(density_obj)) {
      density_val <- density_obj$density_numeric
    }
  }, error = function(e) NULL)
}
```

| Indicator | Value | Threshold | Status |
|-----------|-------|-----------|--------|
| Occurrence Density | `r ifelse(is.na(density_val), "N/A", round(density_val, 3))` | ≥ 0.25 | `r ifelse(!is.na(density_val) && density_val >= 0.25, "✓ PASS", "✗ FAIL")` |
| Inventory Completeness (Chao2) | `r ifelse(is.na(chao2_val), "N/A", round(chao2_val, 3))` | ≥ 0.70 | Pending |
| SAC Slope | TBD | ≤ 0.10 | Pending |

---

# Biodiversity Indicators

## Observed Species Richness

```{r richness-plot, echo=FALSE, fig.height=5}
richness_file <- list.files(
  file.path(output_dir, country, gsub(".*_", "", site_id)),
  pattern = paste0(gsub(".*_", "", site_id), ".*obs_richness.*\\.png$"),
  full.names = TRUE
)

if (length(richness_file) > 0) {
  knitr::include_graphics(richness_file[1])
} else {
  cat("No richness plot available")
}
```

## Total Occurrences

```{r occ-plot, echo=FALSE, fig.height=5}
occ_file <- list.files(
  file.path(output_dir, country, gsub(".*_", "", site_id)),
  pattern = paste0(gsub(".*_", "", site_id), ".*total_occ.*\\.png$"),
  full.names = TRUE
)

if (length(occ_file) > 0) {
  knitr::include_graphics(occ_file[1])
} else {
  cat("No occurrence plot available")
}
```

---

# Data Quality Notes

- This report was automatically generated by the muddymetrics pipeline
- Indicators follow the Troia 2016 methodology for data sufficiency assessment
- For questions, contact the biodiversity monitoring team

---

*Report generated by Muddymetrics v0.1.0*
